Experiences with planning for natural language generation

### 2008-06-19 trunk/Papers/experiences/introduction.tex
more changes to the introduction

We will then discuss some of our experiences using off-the-shelf planners
in these domains. In particular, we explore the efficiency of FF
\cite{HoffmannNebel01} and SGPLAN \cite{hsu06:_new_featur_in_sgplan_for} on
varying-sized instances of our planning domains. We also compare these
results against an ad-hoc Java implementation of GraphPlan.  Our findings
are mixed. On the one hand, it turns out that modern planners handle some
of the search problems that arise in NLG quite easily. (Large problem
instances remain a challenge.) On the other hand, these same planners spend
tremendous amounts of time on preprocessing. For instance, FF spends 90\%
of its runtime in the sentence generation domain on grounding out literals
and actions, and ends up slower than our version of GraphPlan that avoids
grounding. For domains like ours, which are dominated by the number of
actions and the universe size rather than the combinatorics of the search
problem, this observation suggests that the overall runtime of a planner
could be improved by grounding more selectively.

>>>>

We will then discuss some of our experiences using off-the-shelf planners
in these domains. In particular, we explore the efficiency of FF
\cite{HoffmannNebel01} and SGPLAN \cite{hsu06:_new_featur_in_sgplan_for} on
varying-sized instances of our planning domains. We also compare these
results against an ad-hoc Java implementation of GraphPlan.  Our findings
are mixed. On the one hand, it turns out that modern planners handle some
of the search problems that arise in NLG quite easily (although large
problem instances remain a challenge). On the other hand, these same
planners spend tremendous amounts of time on preprocessing. For instance,
FF spends 90\% of its runtime in the sentence generation domain on
grounding out literals and actions, and ends up slower than our version of
GraphPlan that avoids grounding. For domains like ours, which are dominated
by the number of actions and the universe size, rather than the
combinatorics of the search problem, this observation suggests that the
overall runtime of a planner could be improved by grounding more
selectively. We therefore offer these domains as challenges for the
planning community.
